Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2017-05-25 answer-to-reviewers.tex

\smallskip

\emph{In both cases, it is optimal to continuously update the component model parameters.
This is exemplarily shown in the case study in Section~6, with more systematic evidence given in Section~7.
In Section~6.2, the case of failures happening later than expected, i.e., a pessimistic prior is considered,
and the last paragraph before Section~6.3 (beginning with ``The effect of the continuous parameter update \ldots'')
gives a detailed explanation.
Section~6.3 studies a case with failure times earlier than expected, i.e., with too optimistic prior.
Here, as described in the text, both the approach with and without continuous parameter update
trigger maintenance at the same time, leading to the same costs.
However, Figure~8 shows that without continuous parameter update, the system RLD is overestimated,
which may lead to an excess risk of system failure.
***This is confirmed in the simulation study in Section~7.2, Figure~11 (previously Figure~10),
where the continuous update approach (CBM-cpu) can be seen to lead to slightly lower mean cost rates
than the approach without continuous parameter update (CBM-epu and CBM-npu).\\
%
***new simulation scenario to illustrate this!***\\
%
***Citing the last sentence of Section~7,
``[o]verall, it seems that CBM-cpu can play ***exert?*** its adaptive strengths most effectively
when prior assumptions are too pessimistic,
while also performing well when prior assumptions are correct or too optimistic.''\\
%
***impossible to know beforehand if priors too optimistic or too pessimistic***}
%
\item For the example system, I think we can simply use the key stone method (use H as the key stone) to calculate the system reliability when the components are independent.  Is it necessary to use system signature?

\smallskip

\emph{The example system was deliberately chosen to be very simple,
and for such a system, indeed a simpler methodology like the keystone method can very well suffice.
However, our survival signature based method is also applicable for much larger systems with complex structures,
for which the keystone method is not practical anymore,
see, e.g., \citet[Table~2]{2017:reed}.
Furthermore, the \textsf{R} package \texttt{ReliabilityTheory} allows to automatically calculate the
survival signature from any given system graph.}
%no one component can be singled out as the reliability-limiting force.\\
%***add a note on simplicity (to understand what's going on) at example intro in Section~3?***}
\end{enumerate}

### 2017-05-25 cbm-rbd-paper.tex
SDFs comments part 1

The cost-optimal moment of replacement for the system is obtained by minimizing
the expected cost rate per unit of time.
The unit cost rate is recalculated when components fail
or at the end of every (very short) fixed inter-inspection interval***,
leading to a dynamic maintenance policy,
since the aging of components and possible failures will change the cost-optimal moment of replacement in the course of time.
Via numerical experiments, some insight into the performance of the policy is given.
\end{abstract}

@@

Both in practice and academics,
there is a growing interest in condition-based maintenance (CBM), see e.g.,
\citet{2017:oldekeizer}
The central idea behind CBM is to maintain systems or components at exactly the right time,
i.e., just before they fail, %but not too early,
in order to keep their reliability high and operating costs low.
In this context a trade-off is made between the risk of failure during operation
(which can lead to costly downtime: idle workforce, missed production, penalties, loss of reputation)
and the costs of premature maintenance (wasting potential component or system lifetime,
downtime cost, cost of executing unnecessary maintenance activities).

@@

In this paper, we propose a new kind of inspection-based CBM policy*** (drop inspection-based???***)
for when no such \emph{usual} degradation signal for the system is available,
but where the status (working or not working) of the system's components can be monitored (quasi-) continuously.
%i.e., observed every $\delta$ time units, where $\delta$ is very small compared to the lifetimes of components. 
In this situation, one can use the system's reliability block diagram
and information with respect to the status of its components
to directly calculate the system residual life distribution (RLD),
and base the maintenance policy for the system on this distribution.
In fact, our CBM policy can also be seen as based on a multivariate degradation signal,
where each component sends a binary signal, and the reliability block diagram is used for sensor fusion.

In our new policy, there are three types of triggers to review the system:
(1) at the end of each very short time interval $\delta$ 
(where $\delta$ is very short compared to the lifetimes of components),
(2) directly after the failure of a component where the system still functions,
and (3) directly after the failure of a component due to which the system as a whole no longer can function. 
We denote each review of the system in reaction to triggers (1) and (2) by `evaluation',
since the system RLD is re-evaluated at each of these time points,
and a decision is made on whether preventive maintenance should be carried out or not.
We use the term `evaluation' in place of the term `inspection',
because the re-evaluation of the system RLD does not require a physical inspection,
as we assume to learn of the exact failure times of components online via continuous monitoring.

In case of a trigger of type (1),
the currently used models for component failure times are updated
to account for the aging of components,
and the extra lifetime observed for the components.
The latter information is taken into account via right-censored observations
in a Bayesian parameter update step.
In case of a trigger of type (2),
where a component has failed but the system is still functioning,
in addition to the component models also the reliability block diagram of the system is updated.
Based on the above changes,
it is determined in both cases whether the system should be replaced now,
or that this decision should be postponed until the next planned evaluation moment,
accepting the risk of a system breakdown before.
To determine the latter,
we calculate the `optimal' next evaluation moment %moment for system replacement***
based on minimizing the expected maintenance-related cost per per unit of time for the present operational cycle,
where an operational cycle starts with a new system, and ends after this system has been replaced by an as good as new system.

When the `optimal' next evaluation moment is before the next planned evaluation moment, we replace the system now;
else we wait for the next planned evaluation moment.
The reason behind this decision is that $\delta$ is taken as %usually is 
%the shortest interval for which re-evaluation of the system RLD will show any difference***
%the shortest inter-observation period that can be realized from a hardware point of view.
the shortest inter-evaluation period that can be realized from a hardware point of view*** / 
the time granularity according to which maintenance actions can be reasonably triggered***.
To illustrate, for components with lifetimes measuring in a few days,
$\delta$ could be in the order of minutes;
for components with lifetimes measuring in months,
$\delta$ could be one day.

Note that strictly speaking, this decision procedure may not be optimal.
However, because $\delta$ is very small when compared to the prior estimates of the lifetime of the components,
at the time that the next `optimal' observation moment is before the next observation of the status of the still active components,
we usually already have done much better than without updating as described in this paper.

In this context it is also important to realize that our method
doesn't necessarily result in the actual optimal replacement solution for another reason,
inherent to using updated information for decisions,
when these updates can indicate that the former estimates were too optimistic or pessimistic.
The reason for this is that for some components,
a too pessimistic prior probability density function (pdf)
may lead to an increase in system reliability over time without any intervention.
Whether or not this will be the case, as well as until when this kind of increase can occur,
is uncertain at every moment in time.
(***As a sidenote,
this kind of uncertainty about the probabilistic behaviour itself is very often neglected in operations research literature.***)
Determining the next `optimal' evaluation moment can thus only indicate whether or not waiting with the replacement
may result in lower or higher cost per unit of time,
i.e., only indicates a local optimum,
but not necessarily a global one.

@@

***While we also use a Bayesian approach to provide exact expressions for the RLD,***
one of the main differences between \citet{2013:si-et-al} and our paper
is that we use component status data and the system reliability block diagram instead of a continuous degradation signal
as basis for calculating the system RLD.
Another main difference is that our policy can be applied to arbitrary system configurations
(i.e., arbitrary reliability block diagrams with arbitrary components),
whereas the method given by \citet{2013:si-et-al} can only be applied to single components.
A third difference concerns how the cost rate is calculated.
\citet{2013:si-et-al} calculate this rate using the renewal-reward theory approximation.
Essential for using the renewal-reward theory for calculating the expected cost per unit of time
is that the relevant characteristics of the system considered and its environment are not changing,
i.e.\ that the failure behavior of the system,
in essence its relibability function, does not change over time,
and that the same policy with the same parameter values is used for a statistically long enough period of time.
However, due to the update method related to the CBM policy presented in this paper, %like in \citet{2013:si-et-al},
we cannot use the renewal-reward theory based calculation method,
and therefore use the exact formula for the average cost per unit of time.

@@

We can analyze systems with an arbitrary reliability block diagram,
consisting of components of $K$ different types,
where there are $N_k$ exchangeable components of type $k$ in the system,
and the total number of components in the system is $\sum_{k=1}^K N_k = N$.

As a running example, we consider a simplified automotive braking system
consisting of four component types $M$, $H$, $C$ and $P$,
with the reliability block diagram as depicted in Figure~\ref{fig:brakesys-layout}.
The master brake cylinder ($M$) activates all four wheel brake cylinders ($C_1$ -- $C_4$),
which in turn actuate a braking pad assembly each ($P_1$ -- $P_4$).
The hand brake mechanism ($H$) directly actuates the brake pad assemblies $P_3$ and $P_4$;
the vehicle brakes when at least one brake pad assembly is actuated.
Note that because of the `handbrake shortcut', this system cannot be described as a nesting of series and parallel subsystems.
%This system is observed until time $\tnow$,
%leading to censored observation of certain component lifetimes within the system.
***Our example system is deliberately kept quite simple for didactical reasons.
The survival signature allows to analyze much larger systems ***citations***,
and our approach is able to deal with such systems.***

@@

In this section, we describe how the system reliability function $\Rsysnow(t)$ at current time $\tnow$ 
can be calculated for a specific choice of component model.
%Section~\ref{sec:policy} will then show how an adaptive maintenance policy
%can be derived for a monitored system based on such a current system residual life distribution.

@@

By using the Bayesian approach described in Section~\ref{sec:weibull},
our component model allows to include both expert assessments and test data (if available),
and furthermore can account for component lifetime information from the current operational cycle up to $\tnow$.
%***component model: weibull with fixed shape,
%inverse gamma prior on scale parameter,
%fix priors via expected lifetime and prior strength,
%test data inclusion
%with noninformatiove right-censoring
%
In Section~\ref{sec:postpred} we derive the posterior predictive distribution
for the Weibull component model as needed for the current system reliability calculation.
Finally, in Section~\ref{sec:sysreltnow}, we adapt the method from Section~\ref{sec:sysrel} for the adaptive setting,
resulting in a formula for $\Rsysnow(t)$.
%***output is $\Rsysnow(t)$, the current (at time $\tnow$) system reliability function
%(residual life distribution, RLD)
%taking into account the current system state,
%including the current ages of system components, 
%and the lifetime histories of all component types,
%including test data (if available) and expert assessments.

@@

Now that we can calulate the component posterior predictive distributions at $\tnow$,
we can use the method from Section~\ref{sec:sysrel}
to determine the system residual life distribution (RLD) $\Rsysnow(t)$,
giving us the probability that the system functions at times $t > \tnow$,
taking into account all information available at $\tnow$:
\begin{align}
\Rsysnow(t) &= \sum_{l_1=0}^{c_1^{(\tnow)}} \cdots \sum_{l_K=0}^{c_K^{(\tnow)}} \Phinow(l_1,\ldots,l_K)
               \prod_{k=1}^K P(C^k_t = l_k\mid\nkz,\ykz, \vectknow)\,.
\label{eq:sysrel-tnow}
\end{align}
Since this is the distribution of system reliability conditional on the system surviving until $\tnow$,
we have that $\Rsysnow(\tnow) = 1$ for any $\tnow$ before system failure.
Note that if one or several components have failed by $\tnow$,
the system reliability block diagram changes, and with it the survival signature $\Phi(l_1,\ldots,l_K)$.
We denote the current survival signature by $\Phinow(l_1,\ldots,l_K)$.

@@

%***start with $\tausnow$???
Now we can derive the adaptive and dynamic maintenance policy
that resembles a CBM policy.
Our idea is described here first in general terms,
and then illustrated along two examplary timelines in Section~\ref{sec:policy-example}.
Afterwards, we introduce the formal definition of the policy in Section~\ref{sec:operationalprocedure}***,
and give further details on the involved computations in Sections~\ref{sec:costrate} and \ref{sec:optim}.***

@@

The near*** optimal time to system re-evaluation $\tausnow$ is determined based on $\Rsysnow(t)$
by minimizing $\gnow(\tau)$, the expected cost rate for the current operational cycle.
%An operational cycle begins with system start-up,
%and ends when either preventive maintenance is carried out,
%or a failure of the system occurs, with subsequent corrective maintenance.
This criterion, as detailed in Section~\ref{sec:costrate},
%only assumes that $\Rsysnow(t)$ is given,
only assumes that a RLD is given,
and thus is not tied to our choice for the component models.
One could also consider alternative optimality criteria to determine $\tausnow$;
when safety is paramount one could, e.g., determine $\tausnow$ such that
the probability of system failure is at most at some very low pre-determined level.

@@

Figure~\ref{fig:timeline} shows two examplary time lines,
starting each with a new system (operational cycle) at $t=0$.
The left timeline leads to preventive maintenance,
the timeline on the right to corrective maintenance.

As described in Section~\ref{intro},
the health of the system is re-evaluated at three types of triggers.
Triggers of type (1) are the evenly spaced planned evaluation time points $m\delta$, where $m \in \naturals_0$,
giving the time granularity at which maintenance actions can be reasonably initiated.***
%Let $\tthresh$ be a threshold time span chosen for practical reasons.
%used to decide when maintenance is initiated, i.e.,
%a time span chosen to reflect operational practicalities.
The times $m\delta$ are indicated by vertical tick lines on the time axis in Figure~\ref{fig:timeline},
where $\delta = 0.1$.
The moments of failure of a component form the other two types of triggers.
A component failure after which the system still functions is a trigger of type (2),
depicted as a (non-filled) circle on the time axis.
A filled circle indicates a trigger of type (3),
which is a component failure that causes the whole system to fail.

>>>>

The cost-optimal moment of replacement for the system is obtained by minimizing
the expected cost rate per unit of time.
The unit cost rate is recalculated when components fail
or at the end of every (very short) fixed inter-monitoring*** interval,
leading to a dynamic maintenance policy,
since the aging of components and possible failures will change the cost-optimal moment of replacement in the course of time.
Via numerical experiments, some insight into the performance of the policy is given.
\end{abstract}

@@

Both in practice and academics,
there is a growing interest in condition-based maintenance (CBM), see e.g.,
\citet{2017:oldekeizer}
The central idea behind CBM is to maintain systems or components at exactly the right time,
i.e., just before they fail, %but not too early,
in order to keep their reliability high and operating costs low,
using information about the actual condition of the systems or components.
In this context a trade-off is made between the risk of failure during operation
(which can lead to costly downtime: idle workforce, missed production, penalties, loss of reputation)
and the costs of premature maintenance (wasting potential component or system lifetime,
downtime cost, cost of executing unnecessary maintenance activities).

@@

In this paper, we propose a new kind of CBM policy
for when no such \emph{usual} degradation signal for the system is available,
but where the status (working or not working) of the system's components can be monitored (quasi-) continuously.
%i.e., observed every $\delta$ time units, where $\delta$ is very small compared to the lifetimes of components. 
In this situation, one can use the system's reliability block diagram
and information with respect to the status of its components
to directly calculate the system residual life distribution (RLD),
and base the maintenance policy for the system on this distribution.
In fact, our CBM policy can also be seen as based on a multivariate degradation signal,
where each component sends a binary signal, and the reliability block diagram is used for sensor fusion.

In our new policy, there are three types of triggers to review the system:
(1) at the end of each very short time interval $\delta$ 
(where $\delta$ is very short compared to the lifetimes of components),
(2) directly after the failure of a component where the system still functions,
and (3) directly after the failure of a component due to which the system as a whole no longer can function. 
We denote each review of the system in reaction to triggers (1) and (2) by `evaluation',
since the system RLD is re-evaluated at each of these time points,
and a decision is made on whether preventive maintenance should be carried out or not.
We use the term `evaluation' in place of the term `inspection',
because the re-evaluation of the system RLD does not require a physical inspection,
as we assume to learn of the exact failure times of components online via (quasi-) continuous monitoring.

In case of a trigger of type (1),
the currently used models for component failure times are updated
to account for the extra lifetime observed for the components.
This information is taken into account via right-censored observations
in a Bayesian parameter update step.
In case of a trigger of type (2),
where a component has failed but the system is still functioning,
in addition to the component models also the reliability block diagram of the system is updated.
Based on the above changes,
it is determined in both cases whether the system should be replaced now,
or that this decision should be postponed until the next planned evaluation moment,
accepting the risk of a system breakdown before.
To determine the latter,
we calculate the `optimal' next evaluation moment %moment for system replacement***
based on minimizing the expected maintenance-related cost per per unit of time for the present operational cycle,
where an operational cycle starts with a new system, and ends after this system has been replaced by a new system.

When the `optimal' next evaluation moment is before the next planned evaluation moment, we replace the system now;
else we wait for the next planned evaluation moment.
The reason behind this decision is that $\delta$ is taken as %usually is 
%the shortest interval for which re-evaluation of the system RLD will show any difference***
%the shortest inter-observation period that can be realized from a hardware point of view.
the shortest inter-evaluation period that can be realized from a hardware point of view. 
%the time granularity according to which maintenance actions can be reasonably triggered***.
To illustrate, for components with lifetimes amounting to a few days,
$\delta$ could be in the order of minutes;
for components with lifetimes measuring in months,
$\delta$ could be one day.

Note that strictly speaking, this decision procedure may not be optimal.
However, because $\delta$ is very small when compared to the prior estimates of the lifetime of the components,
at the time that the next `optimal' evaluation moment is before the next planned evaluation moment,
we usually already have done much better than without updating as described in this paper.

In this context it is also important to realize that our method
doesn't necessarily result in the actual optimal replacement solution for another reason,
inherent to using updated information for decisions,
when these updates can indicate that the former estimates were too optimistic or too pessimistic.
The reason for this is that for some components,
a too pessimistic prior probability density function (pdf)
may lead to an increase in system reliability over time without any intervention.
Whether or not this will be the case, as well as until when this kind of increase can occur,
is uncertain at every moment in time.
As a sidenote,
this kind of uncertainty about the probabilistic behaviour itself is very often neglected in operations research literature.
Determining the next `optimal' evaluation moment can thus only indicate whether or not waiting with the replacement
may result in lower or higher cost per unit of time,
i.e., only indicates a local optimum,
but not necessarily a global one.

@@

While we also use a Bayesian approach with conjugate priors to provide exact expressions for the RLD,
one of the main differences between \citet{2013:si-et-al} and our paper
is that we use component status data and the system reliability block diagram instead of a continuous degradation signal
as basis for calculating the system RLD.
Another main difference is that our policy can be applied to arbitrary system configurations
(i.e., arbitrary reliability block diagrams with arbitrary components),
whereas the method given by \citet{2013:si-et-al} can only be applied to single components.
A third difference concerns how the cost rate is calculated.
\citet{2013:si-et-al} calculate this rate using the renewal-reward theory approximation.
Essential for using the renewal-reward theory for calculating the expected cost per unit of time
is that the relevant characteristics of the system considered and its environment are not changing,
i.e.\ that the failure behavior of the system,
in essence its relibability function, does not change over time,
and that the same policy with the same parameter values is used for a statistically long enough period of time.
However, due to the update method related to the CBM policy presented in this paper, %like in \citet{2013:si-et-al},
we cannot use the renewal-reward theory based calculation method,
and therefore use the exact formula for the average cost per unit of time.

@@

We can analyze systems with an arbitrary reliability block diagram,
consisting of components of $K$ different types,
where there are $N_k$ exchangeable components of type $k$ in the system,
and $N$, the total number of components in the system, is given by $\sum_{k=1}^K N_k = N$.

As a running example, we consider a simplified automotive braking system
consisting of four component types $M$, $H$, $C$ and $P$,
with the reliability block diagram as depicted in Figure~\ref{fig:brakesys-layout}.
The master brake cylinder ($M$) activates all four wheel brake cylinders ($C_1$ -- $C_4$),
which in turn actuate a braking pad assembly each ($P_1$ -- $P_4$).
The hand brake mechanism ($H$) directly actuates the brake pad assemblies $P_3$ and $P_4$,
and the vehicle brakes when at least one brake pad assembly is actuated.
Note that because of the `handbrake shortcut', this system cannot be described as a nesting of series and parallel subsystems.
%This system is observed until time $\tnow$,
%leading to censored observation of certain component lifetimes within the system.
Our example system is deliberately kept quite simple for didactical reasons.
The survival signature allows to analyze much larger systems,
see, e.g., the examples in \citet{2017:reed},
and our approach is able to deal with such systems.

@@

In this section, we describe how the system reliability function $\Rsysnow(t)$ at current time $\tnow$ 
can be calculated for a specific component model.
%Section~\ref{sec:policy} will then show how an adaptive maintenance policy
%can be derived for a monitored system based on such a current system residual life distribution.

@@

By using the Bayesian approach described in Section~\ref{sec:weibull},
our component model allows to include both expert assessments and test data (if available),
and furthermore can account for component lifetime information from previous operational cycles
and the current operational cycle up to $\tnow$.
%***component model: weibull with fixed shape,
%inverse gamma prior on scale parameter,
%fix priors via expected lifetime and prior strength,
%test data inclusion
%with noninformatiove right-censoring
%
In Section~\ref{sec:postpred} we derive the posterior predictive distribution
for the Weibull component model as needed for the current system reliability calculation.
Finally, in Section~\ref{sec:sysreltnow}, we adapt the method from Section~\ref{sec:sysrel} to the dynamic setting,
resulting in a formula for $\Rsysnow(t)$.
%***output is $\Rsysnow(t)$, the current (at time $\tnow$) system reliability function
%(residual life distribution, RLD)
%taking into account the current system state,
%including the current ages of system components, 
%and the lifetime histories of all component types,
%including test data (if available) and expert assessments.

@@

Now that we can calulate the component posterior predictive distributions at $\tnow$,
we can use the method from Section~\ref{sec:sysrel}
to determine the dynamic system residual life distribution (RLD) $\Rsysnow(t)$,
giving us the probability that the system functions at times $t > \tnow$,
taking into account all information available at $\tnow$:
\begin{align}
\Rsysnow(t) &= \sum_{l_1=0}^{c_1^{(\tnow)}} \cdots \sum_{l_K=0}^{c_K^{(\tnow)}} \Phinow(l_1,\ldots,l_K)
               \prod_{k=1}^K P(C^k_t = l_k\mid\nkz,\ykz, \vectknow)\,.
\label{eq:sysrel-tnow}
\end{align}
Since this is the distribution of system reliability conditional on the system surviving until $\tnow$,
we have that $\Rsysnow(\tnow) = 1$ for any $\tnow$ before system failure.
Note that if one or several components have failed by $\tnow$,
the system reliability block diagram changes, and with it the survival signature $\Phi(l_1,\ldots,l_K)$.
We denote the current survival signature by $\Phinow(l_1,\ldots,l_K)$.

@@

%***start with $\tausnow$???
Now we can derive the adaptive and dynamic maintenance policy
that resembles a CBM policy.
Our idea is described here first in general terms,
and then illustrated along two examplary timelines in Section~\ref{sec:policy-example}.
Afterwards, we give a detailed description of the policy in Section~\ref{sec:operationalprocedure},
and expand on the involved computations in Sections~\ref{sec:costrate} and \ref{sec:optim}.

@@

The optimal time to system re-evaluation $\tausnow$ is determined based on $\Rsysnow(t)$
by minimizing $\gnow(\tau)$, the expected cost rate for the current operational cycle.
%An operational cycle begins with system start-up,
%and ends when either preventive maintenance is carried out,
%or a failure of the system occurs, with subsequent corrective maintenance.
This criterion, as detailed in Section~\ref{sec:costrate},
%only assumes that $\Rsysnow(t)$ is given,
only assumes that a RLD is given,
and thus is not tied to our choice for the component models.
One could also consider alternative optimality criteria to determine $\tausnow$;
when safety is paramount one could, e.g., determine $\tausnow$ such that
the probability of system failure is at most at some very low pre-determined level.

@@

Figure~\ref{fig:timeline} shows two examplary time lines,
starting each with a new system (operational cycle) at $t=0$.
The timeline on the left leads to preventive maintenance,
the timeline on the right to corrective maintenance.

As described in Section~\ref{intro},
the health of the system is re-evaluated at three types of triggers.
Triggers of type (1) are the evenly spaced planned evaluation time points $m\delta$, where $m \in \naturals_0$.
%giving the time granularity at which maintenance actions can be reasonably initiated.***
%Let $\tthresh$ be a threshold time span chosen for practical reasons.
%used to decide when maintenance is initiated, i.e.,
%a time span chosen to reflect operational practicalities.
The times $m\delta$ are indicated by vertical tick lines on the time axis in Figure~\ref{fig:timeline},
where $\delta = 0.1$.
The moments of failure of a component form the other two types of triggers.
A component failure after which the system still functions is a trigger of type (2),
depicted as a (non-filled) circle on the time axis.
A filled circle indicates a trigger of type (3),
which is a component failure that causes the whole system to fail.
